---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# MF.matR

This is a repository of tools to be used for analysis of <i>C. elegans</i> behavioral  and calcium imaging data. It's a work in progress intened to mate matlab and R functions.

## Installation

You can install the released version of MF.matR from github with:

``` {r}
devtools::install_github("mikeod38/MF.matR")
```

## Calcium imaging analysis

Often we want to both analyze Ca2+ imaging data from multiple worms and generate summary plots. Main function for this is plotGCaMP_multi(). This function imports either matlab- or imageJ analyzed calcium imagaing date from single worms. 

```{r example, message=TRUE}
library(MF.matR)
# CaData <- plotGCaMP_multi(FileFilter = OP50,
#                           genotype = N2,
#                           cue = hexanol,
#                           nls = TRUE,
#                           center_on_pulse = 'OFF',
#                           startPulse = 29.5,
#                           endPulse = 60.5,
#                           show.plots = FALSE,
#                           matlab = TRUE,
#                           folderPath = here::here("extdata","Ca_imaging","mat_format"))

#?MF.matR::plotGCaMP_multi()

```


